\documentclass{../booknotes}

\usepackage{import}

\booktitle{Introduction to Symplectic Topology}
\bookauthor{Dusa McDuff and Dietrich Soloman}
\notesauthor{Samuel T. Wallace}

\begin{document}

\maketitle

\begin{pubdescrip}
	\indent \indent	Over the last number of years powerful new methods in analysis and topology have led to the development of the modern global theory of symplectic topology, including several striking and important results. The first edition of Introduction to Symplectic Topology was published in 1995. The book was the first comprehensive introduction to the subject and became a key text in the area. A significantly revised second edition was published in 1998 introducing new sections and updates on the fast-developing area. This new third edition includes updates and new material to bring the book right up-to-date.
\end{pubdescrip}

\begin{transcribernote}
	\indent These notes were taken as part of an independent study course at the University of Florida in Fall 2019. This book was suggested to me as I learned about symplectic geometry and made some comments on the properties of symplectic structures. I have not touched these notes in a while and will probably not return to them soon. \\
	\indent These notes assume familiarity with a wide range of math: modern differential geometry (vector bundles, complex geometry), functional analysis, and algebraic topology (homology and cohomology). It is still possible to get something out of the book without all these prerequisites, since the book covers a wide range of topics. If you are invested in the topic, though, you should think about familiarizing yourself with all the prereqs.
\end{transcribernote}

\tableofcontents

\import{./}{ch2.tex}
\import{./}{ch3.tex}


\end{document}
