\documentclass{../booknotes}

\usepackage{import}

\booktitle{Spectral Methods: Algorithms, Analysis, and Applications}
\bookauthor{Jie Shen, Tao Tang, Li-Lian Wang}
\notesauthor{Samuel T. Wallace}

\begin{document}

\maketitle
\begin{pubdescrip}

	\indent Along with finite differences and finite elements, spectral methods are one of the three main methodologies for solving partial differential equations on computers. This book provides a detailed presentation of basic spectral algorithms, as well as a systematical presentation of  basic convergence theory and error analysis for spectral methods. Readers of this book will be exposed to a unified framework for designing and analyzing spectral algorithms for a variety of problems, including in particular high-order differential equations and problems in unbounded domains. The book contains a large number of figures which are designed to illustrate various concepts stressed in the book. A set of basic matlab codes has been made available online to help the readers to develop their own spectral codes for their specific applications.
\end{pubdescrip}

\begin{transcribernote}
	\indent These notes were taken over summer 2020 as part of self-study preparing for PhD in applied math and numerical analysis. I am reading this without much interpolation theory knowledge, and some prior exposure to spectral methods through Trefethen's book \textit{Spectral Methods in MATLAB} (sorry, no notes for that book). This book comes from a suggestion by a professor as my grad school, and it looked temptingly challenging.
\end{transcribernote}

\tableofcontents


\import{./}{ch1.tex}

\end{document}
